Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-01-27 paper-new/extensional-model.tex
more space squeeze

\begin{enumerate}
\item A cartesian category $\mathcal V$
\item A category $\mathcal E$
\item An action of $\mathcal V^{op}$ (with the $\mathcal V$ cartesian
  product as monoidal structure) on $\mathcal E$. We write this with
  an arrow $A \arr B$.

  This means we have 
  \[ \alpha : {A_1 \times A_2} \arr B \cong A_2 \arr (A_1 \arr B) \]
  and
  \[ i : 1 \arr B \cong B \]
  satisfying coherence isomorphisms.
\item A functor $U : \mathcal E \to \mathcal V$ that ``preserves
  powering'' in that every $U(A \arr B)$ is an exponential of $UB$ by $A$
  and that $U\alpha$ and $Ui$ are mapped to the canonical isomorphisms
  for exponentials.
\item A left adjoint $F \dashv U$
\end{enumerate}

>>>>

\begin{enumerate}
\item A cartesian category $\mathcal V$ and a category $\mathcal E$.
\item An action of $\mathcal V^{op}$ (with the $\mathcal V$ cartesian
  product as monoidal structure) on $\mathcal E$. We write this with
  an arrow $A \arr B$.
  This means we have natural isomorphisms
  $\alpha : {A_1 \times A_2} \arr B \cong A_2 \arr (A_1 \arr B)$ and $i : 1 \arr B \cong B$ satisfying pentagon and triangle identities\cite{action}.
\item $F \dashv U$ where $U : \mathcal E \to \mathcal V$ such that $U$ ``preserves
  powering'' in that every $U(A \arr B)$ is an exponential of $UB$ by $A$
  and that $U\alpha$ and $Ui$ are mapped to the canonical isomorphisms
  for exponentials.
\end{enumerate}
